Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area.

### 2022-07-06 outputs/paper/paper.qmd
Update paper.qmd

I'm interested in finding the trends of the maximum temperatures from 2002 to 2022 by the Month and Year.

@@

@@

Figure 4 shows an ... pattern for the mean pollution from year 2002 to 2020 for NO, NO2, O3, and SO2 by year.

@@

Figure 5 shows an ... pattern for the mean pollution from year 2002 to 2020 for CO by year.

>>>>

I'm interested in finding the trends of the maximum temperatures from 2002 to 2022 by the month and year.

@@

I'm interested in finding the trends of the mean pollution levels from 2002 to 2020 by year. The units of NO, NO2, O3, and SO2 are the same (ppb) whereas the units for CO are different (ppm). For this reason, these plots have been made with regards to those units.

@@

Figure 4 shows an decreasing pattern for the mean pollution from year 2002 to 2020 for NO by year. We can notice that O3 and SO2 levels remain mostly the same throughout the years.

@@

Figure 5 shows a decreasing pattern for the mean pollution from year 2002 to 2020 for CO by year.
